---
title: "Reputation penalty - study 2"
author: "Jacob Ausubel, Annika Davies, and Ethan Porter"
date: "2024-01-16"
output:
  pdf_document:
    extra_dependencies: float
  word_document: default
  html_document:
    df_print: paged
fontsize: 12pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Study 2

Note that we ran two waves for Study 2. We're publicly sharing a dataset in which the two wave datasets have already been merged together and personally identifying information has been removed.

```{r, include = FALSE, message = FALSE}
#Clear global environment
rm(list = ls())
```

```{r, include = FALSE, message = FALSE}
#Loading various packages
library(readr)
library(lmtest)
library(sandwich)
library(margins)
library(texreg)
library(haven)
library(MASS)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(marginaleffects)
library(estimatr)
library(imputeTS)
library(fabricatr)
library(tidyr)
library(tidyverse)
library(lubridate)
library(qualtRics)
library(naniar)
library(RCT)
library(texreg)
library(huxtable)
library(stargazer)
library(ggpubr)
library(vtable)
library(cobalt)
library(kableExtra)
library(xtable)
library(ggthemes)
library(stats)
```

```{r, include = FALSE, message = FALSE}
#Reading in wave 1 dataset; not including first two rows, since those are giving descriptions of
  #the variables
#abortion_wave1_s2_private <- read_csv("January 2024 Screener_February 27, 2024_20.40.csv")
#abortion_wave1_s2_public <- abortion_wave1_s2_private[-c(1,2),]

#Dropping some variables that won't be included in the public dataset
#Note that I'll drop participantId once I've merged wave 1 with wave 2 for Study 2
#abortion_wave1_s2_public <-
#  abortion_wave1_s2_public %>%
#  select(-c(Status, IPAddress, ResponseId, RecipientLastName, RecipientFirstName, 
#         RecipientEmail, ExternalReference, LocationLatitude, LocationLongitude, 
#         DistributionChannel, Q1, ac1, ac2, state, Q45, assignmentId, projectId))
```

```{r, include = FALSE, message = FALSE}
#Recoding variable names so that they end with _w1
#colnames(abortion_wave1_s2_public) <-
#  paste0(colnames(abortion_wave1_s2_public), "_w1")

#However, I want one column to be participantId, NOT participantId_w1
#That way, I can merge the wave 1 and wave 2 datasets together
#colnames(abortion_wave1_s2_public)[
#  colnames(abortion_wave1_s2_public) == "participantId_w1"] <- "participantId"
```

```{r, include = FALSE, message = FALSE}
#Reading in wave 2 dataset
#abortion_wave2_s2_private <- read_csv("Abortion Study 2 EP version_February 27, 2024_20.26.csv")
```

```{r, include = FALSE, message = FALSE}
#Subsetting to actual survey respondents and people who consented to take
  #the survey
#abortion_wave2_s2_public <-
#  subset(abortion_wave2_s2_private, Status == "IP Address" & Q1...18 == "Yes")

#Dropping some variables that won't be included in the public dataset
#Note that I'll drop participantId once I've merged wave 1 with wave 2 for Study 2
#abortion_wave2_s2_public <-
#  abortion_wave2_s2_public %>%
#  select(-c(Status, IPAddress, ResponseId, RecipientLastName, RecipientFirstName, 
#            RecipientEmail, ExternalReference, LocationLatitude, LocationLongitude, 
#            DistributionChannel, Q1...18, Q2_Browser, Q2_Version, `Q2_Operating System`, 
#            Q2_Resolution, assignmentId, projectId))
```

```{r, include = FALSE, message = FALSE}
#Recoding variable names so that they end with _w2
#colnames(abortion_wave2_s2_public) <-
#  paste0(colnames(abortion_wave2_s2_public), "_w2")

#However, I want one column to be participantId, NOT participantId_w2
#That way, I can merge the wave 1 and wave 2 datasets together
#colnames(abortion_wave2_s2_public)[
#  colnames(abortion_wave2_s2_public) == "participantId_w2"] <- "participantId"
```


```{r, include = FALSE, message = FALSE}
#Merging together wave 1 and wave 2
#Only people kept: people in which there is a common participant ID
  #in both waves
#both_waves_s2 <-
#  merge(abortion_wave1_s2_public, abortion_wave2_s2_public, by = c("participantId"))

#Dropping participantId variable
#both_waves_s2 <-
#  both_waves_s2 %>%
#  select(-participantId)
```

```{r, include = FALSE, message = FALSE}
#Creating public CSV file
#write.csv(both_waves_s2, "both_wave_s2 - PUBLIC.csv", row.names = FALSE)
```

```{r, include = FALSE, message = FALSE}
#Clear global environment
rm(list = ls())
```

```{r, include = FALSE, message = FALSE}
#Reading in public dataset that includes both waves of Study 2
both_waves_s2 <- read_csv("both_wave_s2 - PUBLIC.csv")
```

```{r, include = FALSE, message = FALSE}
#Creating cleaned PID variable (screener/wave 1)
#1 (Strong Democrat) to 7 (Strong Republican)
both_waves_s2$pid_cleaned <- NA
both_waves_s2$pid_cleaned[
  both_waves_s2$pid_dem_w1 == "Strong Democrat"
  ] <- 1
both_waves_s2$pid_cleaned[
  both_waves_s2$pid_dem_w1 == "Not very strong Democrat"
  ] <- 2
both_waves_s2$pid_cleaned[
  both_waves_s2$pid_indep_w1 == "Closer to the Democratic Party"
  ] <- 3
both_waves_s2$pid_cleaned[
  both_waves_s2$pid_indep_w1 == "Neither"
  ] <- 4
both_waves_s2$pid_cleaned[
  both_waves_s2$pid_indep_w1 == "Closer to the Republican Party"
  ] <- 5
both_waves_s2$pid_cleaned[
  both_waves_s2$pid_rep_w1 == "Not very strong Republican"
  ] <- 6
both_waves_s2$pid_cleaned[
  both_waves_s2$pid_rep_w1 == "Strong Republican"
  ] <- 7
```

```{r, include = FALSE, message = FALSE}
#Creating male dummy variable
both_waves_s2$male <- ifelse(both_waves_s2$gender_w1 == "Man", 1, 0)
```

```{r, include = FALSE, message = FALSE}
#Creating a dummy variable for whether someone has a Bachelor's
  #degree or above
both_waves_s2$college_grad <-
  ifelse(both_waves_s2$educ_w1 %in% 
    c("Bachelor's degree", "Master's degree", "Professional or doctorate degree"), 
    1, 0)
```

```{r, include = FALSE, message = FALSE}
#Household income at $100,000+
both_waves_s2$income_100000 <-
  ifelse(both_waves_s2$income_w1 %in%
    c("$100,000 to less than $200,000", "$200,000 to less than $250,000", 
    "Greater than $250,000"),
    1, 0)
```

```{r, include = FALSE, message = FALSE}
#Cleaning birth year variable
both_waves_s2$birthyear_w1 <-
  as.numeric(both_waves_s2$birthyear_w1)
both_waves_s2$birthyear_w1[
  both_waves_s2$birthyear_w1 == 199
  ] <- NA
both_waves_s2$birthyear_w1[
  both_waves_s2$birthyear_w1 == 66
  ] <- 2024-66
both_waves_s2$birthyear_w1[
  both_waves_s2$birthyear_w1 == 29
  ] <- 2024-29
both_waves_s2$birthyear_w1[
  both_waves_s2$birthyear_w1 == 32
  ] <- 2024-32
both_waves_s2$birthyear_w1[
  both_waves_s2$birthyear_w1 == 38
  ] <- 2024-38
both_waves_s2$birthyear_w1[
  both_waves_s2$birthyear_w1 == 34
  ] <- 2024-34
both_waves_s2$birthyear_w1[
  both_waves_s2$birthyear_w1 == 25
  ] <- 2024-25
both_waves_s2$birthyear_w1[
  both_waves_s2$birthyear_w1 == 43
  ] <- 2024-43
both_waves_s2$birthyear_w1[
  both_waves_s2$birthyear_w1 == 42
  ] <- 2024-42
both_waves_s2$birthyear_w1[
  both_waves_s2$birthyear_w1 == 11992
  ] <- 1992
both_waves_s2$birthyear_w1[
  both_waves_s2$birthyear_w1 == 19971
  ] <- 1971
both_waves_s2$birthyear_w1[
  both_waves_s2$birthyear_w1 == 1193
  ] <- 1993
both_waves_s2$birthyear_w1[
  both_waves_s2$birthyear_w1 == 33
  ] <- 2024-33
both_waves_s2$birthyear_w1[
  both_waves_s2$birthyear_w1 == 45
  ] <- 2024-45
both_waves_s2$birthyear_w1[
  both_waves_s2$birthyear_w1 == 28390
  ] <- NA
both_waves_s2$birthyear_w1[
  both_waves_s2$birthyear_w1 == 30
  ] <- 2024-30
both_waves_s2$birthyear_w1[
  both_waves_s2$birthyear_w1 == 2990
  ] <- 1990
```

```{r, include = FALSE, message = FALSE}
#Creating age variable
both_waves_s2$age <-
  2024-both_waves_s2$birthyear_w1
```

```{r, include = FALSE, message = FALSE}
#Creating a dummy variable for whether someone is
  #affiliated with a religion
both_waves_s2$relig_affiliated <-
  ifelse(
    both_waves_s2$religion_w1 %in% c("Buddhist", "Jewish", "Mormon", "Muslim", 
    "Orthodox, such as Greek or Russian Orthodox", "Protestant",
    "Roman Catholic", "Something else"), 1, 0
  )
```

```{r, include = FALSE, message = FALSE}
#Creating a dummy variable for whether someone attends
  #religious services at least once a month
both_waves_s2$monthly_attend <-
  ifelse(
    both_waves_s2$religiosity_w1 %in% c("More than once a week",
    "Once a week", "Once or twice a month"), 1, 0
  )
```

```{r, include = FALSE, message = FALSE}
#Creating a dummy variable for whether someone is
  #non-Hispanic White
both_waves_s2$non_hisp_white <-
  ifelse(
    both_waves_s2$race_w1 == "White" & both_waves_s2$hispanic_w1 == "No",
    1, 0
  )
```

```{r, include = FALSE, message = FALSE}
#Recoding first factual belief (screener)
both_waves_s2$fc_1_belief_screener <- NA
both_waves_s2$fc_1_belief_screener[
  both_waves_s2$fc_1_belief_w1 == "Very accurate"
  ] <- 4
both_waves_s2$fc_1_belief_screener[
  both_waves_s2$fc_1_belief_w1 == "Somewhat accurate"
  ] <- 3
both_waves_s2$fc_1_belief_screener[
  both_waves_s2$fc_1_belief_w1 == "Not very accurate"
  ] <- 2
both_waves_s2$fc_1_belief_screener[
  both_waves_s2$fc_1_belief_w1 == "Not at all accurate"
  ] <- 1
```

```{r, include = FALSE, message = FALSE}
#Recoding second factual belief (screener)
both_waves_s2$fc_2_belief_screener <- NA
both_waves_s2$fc_2_belief_screener[
  both_waves_s2$fc_2_belief_w1 == "Very accurate"
  ] <- 4
both_waves_s2$fc_2_belief_screener[
  both_waves_s2$fc_2_belief_w1 == "Somewhat accurate"
  ] <- 3
both_waves_s2$fc_2_belief_screener[
  both_waves_s2$fc_2_belief_w1 == "Not very accurate"
  ] <- 2
both_waves_s2$fc_2_belief_screener[
  both_waves_s2$fc_2_belief_w1 == "Not at all accurate"
  ] <- 1
```

```{r, include = FALSE, message = FALSE}
#Recoding third factual belief (screener)
both_waves_s2$fc_3_belief_screener <- NA
both_waves_s2$fc_3_belief_screener[
  both_waves_s2$fc_3_belief_w1 == "Very accurate"
  ] <- 4
both_waves_s2$fc_3_belief_screener[
  both_waves_s2$fc_3_belief_w1 == "Somewhat accurate"
  ] <- 3
both_waves_s2$fc_3_belief_screener[
  both_waves_s2$fc_3_belief_w1 == "Not very accurate"
  ] <- 2
both_waves_s2$fc_3_belief_screener[
  both_waves_s2$fc_3_belief_w1 == "Not at all accurate"
  ] <- 1
```

```{r, include = FALSE, message = FALSE}
#Recoding abortion laws measure (screener)
both_waves_s2$abortion_laws_screener <- NA
both_waves_s2$abortion_laws_screener[
  both_waves_s2$abortion_laws_w1 == "By law, abortion should never be permitted."
  ] <- 1
both_waves_s2$abortion_laws_screener[
  both_waves_s2$abortion_laws_w1 == "The law should permit abortion only in case of rape, incest or when the woman's life is in danger."
  ] <- 2
both_waves_s2$abortion_laws_screener[
  both_waves_s2$abortion_laws_w1 == "The law should permit abortion for reasons other than rape, incest, or danger to the woman's life, but only after the need has been clearly established."
  ] <- 3
both_waves_s2$abortion_laws_screener[
  both_waves_s2$abortion_laws_w1 == "By law, a woman should always be able to obtain an abortion as a matter of personal choice."
  ] <- 4
```

```{r, include = FALSE, message = FALSE}
#Recoding abortion penalties measure (screener)
both_waves_s2$abortion_penalties_1_cleaned <- NA
both_waves_s2$abortion_penalties_1_cleaned[
  both_waves_s2$abortion_penalties_1_w1 == "Should face penalties"
  ] <- 1
both_waves_s2$abortion_penalties_1_cleaned[
  both_waves_s2$abortion_penalties_1_w1 == "Should not face penalties"
  ] <- 0

both_waves_s2$abortion_penalties_2_cleaned <- NA
both_waves_s2$abortion_penalties_2_cleaned[
  both_waves_s2$abortion_penalties_2_w1 == "Should face penalties"
  ] <- 1
both_waves_s2$abortion_penalties_2_cleaned[
  both_waves_s2$abortion_penalties_2_w1 == "Should not face penalties"
  ] <- 0

both_waves_s2$abortion_penalties_3_cleaned <- NA
both_waves_s2$abortion_penalties_3_cleaned[
  both_waves_s2$abortion_penalties_3_w1 == "Should face penalties"
  ] <- 1
both_waves_s2$abortion_penalties_3_cleaned[
  both_waves_s2$abortion_penalties_3_w1 == "Should not face penalties"
  ] <- 0

both_waves_s2$abortion_penalties_4_cleaned <- NA
both_waves_s2$abortion_penalties_4_cleaned[
  both_waves_s2$abortion_penalties_4_w1 == "Should face penalties"
  ] <- 1
both_waves_s2$abortion_penalties_4_cleaned[
  both_waves_s2$abortion_penalties_4_w1 == "Should not face penalties"
  ] <- 0

both_waves_s2$abortion_penalties_screener <-
  both_waves_s2$abortion_penalties_1_cleaned + 
  both_waves_s2$abortion_penalties_2_cleaned +
  both_waves_s2$abortion_penalties_3_cleaned +
  both_waves_s2$abortion_penalties_4_cleaned 
```

```{r, include = FALSE, message = FALSE}
#Making feeling thermometer variables (from W1/screener) numeric

#Alliance Defending Freedom (screener)
both_waves_s2$alliance_defending_freedom_screener <-
  as.numeric(both_waves_s2$thermometer_1_w1)
#Seth Gruber (screener)
both_waves_s2$gruber_screener <-
  as.numeric(both_waves_s2$thermometer_2_w1)
#Americans United For Life (screener)
both_waves_s2$americans_united_screener <-
  as.numeric(both_waves_s2$thermometer_3_w1)
#Eric Swalwell (screener)
both_waves_s2$swalwell_screener <-
  as.numeric(both_waves_s2$thermometer_5_w1)
#PolitiFact (screener)
both_waves_s2$politifact_screener <-
  as.numeric(both_waves_s2$thermometer_6_w1)
#Planned Parenthood (screener)
both_waves_s2$planned_parenthood_screener <-
  as.numeric(both_waves_s2$thermometer_7_w1)
```

## List of variables

### Main variables

**Factual belief 1**: Belief that abortion pills are dangerous and that 1 in 5 women will suffer a complication (1-to-4 scale)

**Factual belief 2**: Belief that more contraception availability increases abortion demand (1-to-4 scale)

**Factual belief 3**: Belief that if a 10-year-old became pregnant as a result of rape and terminated the pregnancy because it was threatening her life, then that’s not an abortion (1-to-4 scale)

**Various feeling thermometers** (0-to-100 scale)

**Abortion laws measure** (1-to-4 scale)

**Abortion penalties measure** (0-to-4 scale)

### Some control variables

**Partisanship**: 1 (Strong Democrat) to 7 (Strong Republican) scale

**Male**: 1 = Yes, 0 = No

**College graduate**: 1 = Yes, 0 = No

**High household income**: 1 = household income of $100,000+, 0 = below that

**Age**: 18+

**Religiously affiliated**: 1 = Yes, 0 = No

**Attends religious services at least once a month**: 1 = Yes, 0 = No

**Non-Hispanic White**: 1 = Yes, 0 = No


```{r, include = FALSE, message = FALSE}
#Recoding first factual belief (wave 2)
#Belief that abortion pills are dangerous and that 1 in 5 women will suffer a complication
both_waves_s2$fc_1_belief <- NA
both_waves_s2$fc_1_belief[
  both_waves_s2$Q1...31_w2 == "Very accurate"
  ] <- 4
both_waves_s2$fc_1_belief[
  both_waves_s2$Q1...31_w2 == "Somewhat accurate"
  ] <- 3
both_waves_s2$fc_1_belief[
  both_waves_s2$Q1...31_w2 == "Not very accurate"
  ] <- 2
both_waves_s2$fc_1_belief[
  both_waves_s2$Q1...31_w2 == "Not at all accurate"
  ] <- 1
```

```{r, include = FALSE, message = FALSE}
#Making feeling thermometers (FC1, wave 2) numeric

#Alliance Defending Freedom
both_waves_s2$therm_1_fc1 <-
  as.numeric(both_waves_s2$Q1_1...32_w2)
#iPhone
both_waves_s2$therm_2_fc1 <-
  as.numeric(both_waves_s2$Q1_2...33_w2)
#McDonald's
both_waves_s2$therm_3_fc1 <-
  as.numeric(both_waves_s2$Q1_3...34_w2)
#PolitiFact
both_waves_s2$therm_4_fc1 <-
  as.numeric(both_waves_s2$Q1_4...35_w2)
#Planned Parenthood
both_waves_s2$therm_5_fc1 <-
  as.numeric(both_waves_s2$Q1_5...36_w2)
```

```{r, include = FALSE, message = FALSE}
#Setting misinformation group as reference category (for FC1, wave 2)
both_waves_s2$fc1_w2 <- 
  as.factor(both_waves_s2$fc1_w2)
both_waves_s2$fc1_w2 <- 
  relevel(both_waves_s2$fc1_w2, ref="mis")
```

```{r, include = FALSE, message = FALSE}
#Recoding second factual belief (wave 2)
#Belief that more contraception availability increases abortion demand
both_waves_s2$fc_2_belief <- NA
both_waves_s2$fc_2_belief[
  both_waves_s2$Q1...53_w2 == "Very accurate"
  ] <- 4
both_waves_s2$fc_2_belief[
  both_waves_s2$Q1...53_w2 == "Somewhat accurate"
  ] <- 3
both_waves_s2$fc_2_belief[
  both_waves_s2$Q1...53_w2 == "Not very accurate"
  ] <- 2
both_waves_s2$fc_2_belief[
  both_waves_s2$Q1...53_w2 == "Not at all accurate"
  ] <- 1
```

```{r, include = FALSE, message = FALSE}
#Making feeling thermometers (FC2, wave 2) numeric

#Seth Gruber
both_waves_s2$therm_1_fc2 <-
  as.numeric(both_waves_s2$Q1_1...54_w2)
#iPhone
both_waves_s2$therm_2_fc2 <-
  as.numeric(both_waves_s2$Q1_2...55_w2)
#McDonald's
both_waves_s2$therm_3_fc2 <-
  as.numeric(both_waves_s2$Q1_3...56_w2)
#PolitiFact
both_waves_s2$therm_4_fc2 <-
  as.numeric(both_waves_s2$Q1_4...57_w2)
#Planned Parenthood
both_waves_s2$therm_5_fc2 <-
  as.numeric(both_waves_s2$Q1_5...58_w2)
```

```{r, include = FALSE, message = FALSE}
#Setting misinformation group as reference category (for FC2, wave 2)
both_waves_s2$fc2_w2 <- 
  as.factor(both_waves_s2$fc2_w2)
both_waves_s2$fc2_w2 <- 
  relevel(both_waves_s2$fc2_w2, ref="mis")
```

```{r, include = FALSE, message = FALSE}
#Recoding third factual belief (wave 2)
#Belief that if a 10-year-old became pregnant as a result of rape and terminated the pregnancy 
  #because it was threatening her life, then that's not an abortion
both_waves_s2$fc_3_belief <- NA
both_waves_s2$fc_3_belief[
  both_waves_s2$Q1...75_w2 == "Very accurate"
  ] <- 4
both_waves_s2$fc_3_belief[
  both_waves_s2$Q1...75_w2 == "Somewhat accurate"
  ] <- 3
both_waves_s2$fc_3_belief[
  both_waves_s2$Q1...75_w2 == "Not very accurate"
  ] <- 2
both_waves_s2$fc_3_belief[
  both_waves_s2$Q1...75_w2 == "Not at all accurate"
  ] <- 1
```


```{r, include = FALSE, message = FALSE}
#Making feeling thermometers (FC3, wave 2) numeric

#Americans United For Life
both_waves_s2$therm_1_fc3 <-
  as.numeric(both_waves_s2$Q1_1...76_w2)
#Eric Swalwell
both_waves_s2$therm_2_fc3 <-
  as.numeric(both_waves_s2$Q1_2...77_w2)
#iPhone
both_waves_s2$therm_3_fc3 <-
  as.numeric(both_waves_s2$Q1_3...78_w2)
#McDonald's
both_waves_s2$therm_4_fc3 <-
  as.numeric(both_waves_s2$Q1_4...79_w2)
#PolitiFact
both_waves_s2$therm_5_fc3 <-
  as.numeric(both_waves_s2$Q1_5...80_w2)
#Planned Parenthood
both_waves_s2$therm_6_fc3 <-
  as.numeric(both_waves_s2$Q1_6_w2)
```

```{r, include = FALSE, message = FALSE}
#Setting misinformation group as reference category (for FC3, wave 2)
both_waves_s2$fc3_w2 <- 
  as.factor(both_waves_s2$fc3_w2)
both_waves_s2$fc3_w2 <- 
  relevel(both_waves_s2$fc3_w2, ref="mis")
```

## Factual belief models

### Main models

```{r, include = FALSE, message = FALSE}
#First factual belief
#Running model
fit1_s2 <- lm_robust(fc_1_belief ~ fc1_w2 + fc_1_belief_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2)
```

```{r, echo = FALSE, results='asis'}
#Creating regression table
texreg(fit1_s2, include.ci = FALSE,
       custom.coef.names = c("Intercept", "Control", "Fact check", "Pre-treatment factual belief", 
          "Partisanship", "Male", "College graduate", "High household income", "Age", "Religiously affiliated", "Monthly attendance",
          "Non-Hispanic White"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Effect of fact check on the belief that abortion pills are dangerous and that 1 in 5 women will suffer a complication (1-to-4 scale)", 
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
       omit.coef = "fc_1_belief_screener|pid_cleaned|male|college_grad|income_100000|age|relig_affiliated|monthly_attend|non_hisp_white")
```
```{r, include = FALSE, message = FALSE}
#Second factual belief
#Running model
fit2_s2 <- lm_robust(fc_2_belief ~ fc2_w2 + fc_2_belief_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2)
```

```{r, echo = FALSE, results='asis'}
#Creating regression table
texreg(fit2_s2, include.ci = FALSE,
       custom.coef.names = c("Intercept", "Control", "Fact check", "Pre-treatment factual belief", 
          "Partisanship", "Male", "College graduate", "High household income", "Age", "Religiously affiliated", "Monthly attendance",
          "Non-Hispanic White"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Effect of fact check on the belief that more contraception availability increases abortion demand (1-to-4 scale)", 
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
       omit.coef = "fc_2_belief_screener|pid_cleaned|male|college_grad|income_100000|age|relig_affiliated|monthly_attend|non_hisp_white")
```
```{r, include = FALSE, message = FALSE}
#Third factual belief
#Running model
fit3_s2 <- lm_robust(fc_3_belief ~ fc3_w2 + fc_3_belief_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2)
```

```{r, echo = FALSE, results='asis'}
#Creating regression table
texreg(fit3_s2, include.ci = FALSE,
       custom.coef.names = c("Intercept", "Control", "Fact check", "Pre-treatment factual belief", 
          "Partisanship", "Male", "College graduate", "High household income", "Age", "Religiously affiliated", "Monthly attendance",
          "Non-Hispanic White"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Effect of fact check on the belief about the pregnant 10-year-old (1-to-4 scale)", 
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
       omit.coef = "fc_3_belief_screener|pid_cleaned|male|college_grad|income_100000|age|relig_affiliated|monthly_attend|non_hisp_white")
```
### Does receptivity to fact-checks (that is, the correction - misinformation contrast) differ by Party ID?

```{r, include = FALSE, message = FALSE}
#Recoding partisanship variable
both_waves_s2$pid_alternative <- both_waves_s2$pid_1_w1
both_waves_s2$pid_alternative[
  both_waves_s2$pid_1_w1 == "Independent"
  ] <- "Independent/Other"
both_waves_s2$pid_alternative[
  both_waves_s2$pid_1_w1 == "Other"
  ] <- "Independent/Other"
```

```{r, include = FALSE, message = FALSE}
#First factual belief
#Running model
rq1a_s2 <- lm_robust(fc_1_belief ~ fc1_w2*pid_alternative + fc_1_belief_screener +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2)
```

```{r, echo = FALSE, results='asis'}
#Creating regression table
texreg(rq1a_s2, include.ci = FALSE,
       custom.coef.names = 
         c("Intercept", "Control", "Fact check",
           "Independent/Other", "Republican",
           "Pre-treatment factual belief", 
          "Male", "College graduate", 
          "High household income", "Age", "Religiously affiliated", "Monthly attendance",
          "Non-Hispanic White",
           "Control*Independent/Other",
           "Fact check*Independent/Other",
           "Control*Republican",
           "Fact check*Republican"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Interaction between being a Republican/Independent (vs. being a Democrat) and fact check of belief that abortion pills are dangerous (1-to-4 scale)", 
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
       omit.coef = "fc_1_belief_screener|male|college_grad|income_100000|age|relig_affiliated|monthly_attend|non_hisp_white")
```

```{r, include = FALSE, message = FALSE}
#Second factual belief
#Running model
rq1b_s2 <- lm_robust(fc_2_belief ~ fc2_w2*pid_alternative + fc_2_belief_screener +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2)
```

```{r, echo = FALSE, results='asis'}
#Creating regression table
texreg(rq1b_s2, include.ci = FALSE,
       custom.coef.names = 
         c("Intercept", "Control", "Fact check",
           "Independent/Other", "Republican",
           "Pre-treatment factual belief", 
          "Male", "College graduate", 
          "High household income", "Age", "Religiously affiliated", "Monthly attendance",
          "Non-Hispanic White",
           "Control*Independent/Other",
           "Fact check*Independent/Other",
           "Control*Republican",
           "Fact check*Republican"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Interaction between being a Republican/Independent (vs. being a Democrat) and fact check of the belief that more contraception availability increases abortion demand (1-to-4 scale)", 
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
       omit.coef = "fc_2_belief_screener|male|college_grad|income_100000|age|relig_affiliated|monthly_attend|non_hisp_white")
```

```{r, include = FALSE, message = FALSE}
#Third factual belief
#Running model
rq1c_s2 <- lm_robust(fc_3_belief ~ fc3_w2*pid_alternative + fc_3_belief_screener +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2)
```

```{r, echo = FALSE, results='asis'}
#Creating regression table
texreg(rq1c_s2, include.ci = FALSE,
       custom.coef.names = 
         c("Intercept", "Control", "Fact check",
           "Independent/Other", "Republican",
          "Pre-treatment factual belief", 
          "Male", "College graduate", 
          "High household income", "Age", "Religiously affiliated", "Monthly attendance",
          "Non-Hispanic White",
           "Control*Independent/Other",
           "Fact check*Independent/Other",
           "Control*Republican",
           "Fact check*Republican"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Interaction between being a Republican/Independent (vs. being a Democrat) and fact check of the belief about the pregnant 10-year-old (1-to-4 scale)", 
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
       omit.coef = "fc_3_belief_screener|male|college_grad|income_100000|age|relig_affiliated|monthly_attend|non_hisp_white")
```

### Does receptivity to fact-checks (that is, the correction - misinformation contrast) differ by religiosity?

```{r, include = FALSE, message = FALSE}
#Creating new religiosity variable
both_waves_s2$attend_cleaned <- "Low"
both_waves_s2$attend_cleaned[
  both_waves_s2$religiosity_w1 == "A few times a year"
  ] <- "Medium"
both_waves_s2$attend_cleaned[
  both_waves_s2$religiosity_w1 == "Once or twice a month"
  ] <- "Medium"
both_waves_s2$attend_cleaned[
  both_waves_s2$religiosity_w1 == "Once a week"
  ] <- "High"
both_waves_s2$attend_cleaned[
  both_waves_s2$religiosity_w1 == "More than once a week"
  ] <- "High"
both_waves_s2$attend_cleaned <-
  as.factor(both_waves_s2$attend_cleaned)
both_waves_s2$attend_cleaned <- 
  relevel(both_waves_s2$attend_cleaned, ref="Medium")
```

```{r, include = FALSE, message = FALSE}
#First factual belief
#Running model
rq2a_s2 <- lm_robust(fc_1_belief ~ fc1_w2*attend_cleaned + fc_1_belief_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        non_hisp_white, data = both_waves_s2)
```

```{r, echo = FALSE, results='asis'}
#Creating regression table
texreg(rq2a_s2, include.ci = FALSE,
       custom.coef.names = 
         c("Intercept", "Control", "Fact check",
           "High attendance", "Low attendance",
          "Pre-treatment factual belief", 
          "Partisanship", "Male", "College graduate", "High household income", "Age",
          "Non-Hispanic White",
           "Control*High attendance",
           "Fact check*High attendance",
           "Control*Low attendance",
           "Fact check*Low attendance"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Interaction between high/low (vs. medium) religious attendance and fact check of belief that abortion pills are dangerous (1-to-4 scale)", 
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
       omit.coef = "fc_1_belief_screener|pid_cleaned|male|college_grad|income_100000|age|non_hisp_white")
```

```{r, include = FALSE, message = FALSE}
#Second factual belief
#Running model
rq2b_s2 <- lm_robust(fc_2_belief ~ fc2_w2*attend_cleaned + fc_2_belief_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        non_hisp_white, data = both_waves_s2)
```

```{r, echo = FALSE, results='asis'}
#Creating regression table
texreg(rq2b_s2, include.ci = FALSE,
       custom.coef.names = 
         c("Intercept", "Control", "Fact check",
           "High attendance", "Low attendance",
           "Pre-treatment factual belief", 
          "Partisanship", "Male", "College graduate", "High household income", "Age",
          "Non-Hispanic White",
           "Control*High attendance",
           "Fact check*High attendance",
           "Control*Low attendance",
           "Fact check*Low attendance"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Interaction between high/low (vs. medium) religious attendance and fact check of the belief that more contraception availability increases abortion demand (1-to-4 scale)", 
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
       omit.coef = "fc_2_belief_screener|pid_cleaned|male|college_grad|income_100000|age|non_hisp_white")
```

```{r, include = FALSE, message = FALSE}
#Third factual belief
#Running model
rq2c_s2 <- lm_robust(fc_3_belief ~ fc3_w2*attend_cleaned + fc_3_belief_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        non_hisp_white, data = both_waves_s2)
```

```{r, echo = FALSE, results='asis'}
#Regression output (model rq1c_s2)
#Creating regression table
texreg(rq2c_s2, include.ci = FALSE,
       custom.coef.names = 
         c("Intercept", "Control", "Fact check",
           "High attendance", "Low attendance",
           "Pre-treatment factual belief", 
          "Partisanship", "Male", "College graduate", "High household income", "Age",
          "Non-Hispanic White",
           "Control*High attendance",
           "Fact check*High attendance",
           "Control*Low attendance",
           "Fact check*Low attendance"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Interaction between high/low (vs. medium) religious attendance and fact check of the belief about the pregnant 10-year-old (1-to-4 scale)", 
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
       omit.coef = "fc_3_belief_screener|pid_cleaned|male|college_grad|income_100000|age|non_hisp_white")
```

## Attitudinal belief models

### Main models

```{r, include = FALSE, message = FALSE}
#March by Alliance Defending Freedom
#Running model
fit4_s2 <- lm_robust(therm_1_fc1 ~ fc1_w2 + alliance_defending_freedom_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2)
```

```{r, echo = FALSE, results='asis'}
#Creating regression table
texreg(fit4_s2, include.ci = FALSE,
       custom.coef.names = c("Intercept", "Control", "Fact check", "Pre-treatment feeling thermometer", 
          "Partisanship", "Male", "College graduate", "High household income", "Age", "Religiously affiliated", "Monthly attendance",
          "Non-Hispanic White"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Effect of fact check about abortion pills on ratings of Alliance Defending Freedom (0-to-100 scale)", 
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
       omit.coef = "alliance_defending_freedom_screener|pid_cleaned|male|college_grad|income_100000|age|relig_affiliated|monthly_attend|non_hisp_white")
```

```{r, include = FALSE, message = FALSE}
#Seth Gruber
#Running model
fit5_s2 <- lm_robust(therm_1_fc2 ~ fc2_w2 + gruber_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2)
```

```{r, echo = FALSE, results='asis'}
#Creating regression table
texreg(fit5_s2, include.ci = FALSE,
       custom.coef.names = c("Intercept", "Control", "Fact check", "Pre-treatment feeling thermometer", 
          "Partisanship", "Male", "College graduate", "High household income", "Age", "Religiously affiliated", "Monthly attendance",
          "Non-Hispanic White"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Effect of fact check about contraception availability on ratings of Seth Gruber (0-to-100 scale)", 
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
       omit.coef = "gruber_screener|pid_cleaned|male|college_grad|income_100000|age|relig_affiliated|monthly_attend|non_hisp_white")
```

```{r, include = FALSE, message = FALSE}
#Seth Gruber
#Running model
fit6_s2 <- lm_robust(therm_1_fc3 ~ fc3_w2 + americans_united_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2)
```

```{r, echo = FALSE, results='asis'}
#Creating regression table
texreg(fit6_s2, include.ci = FALSE,
       custom.coef.names = c("Intercept", "Control", "Fact check", "Pre-treatment feeling thermometer", 
          "Partisanship", "Male", "College graduate", "High household income", "Age", "Religiously affiliated", "Monthly attendance",
          "Non-Hispanic White"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Effect of fact check about pregnant 10-year-old on ratings of Americans United For Life (0-to-100 scale)", 
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
       omit.coef = "americans_united_screener|pid_cleaned|male|college_grad|income_100000|age|relig_affiliated|monthly_attend|non_hisp_white")
```

### Attitudes by partisanship

```{r, include = FALSE, message = FALSE}
#Alliance Defending Freedom - by partisanship
#Running models

#Democrats
fit7_s2_dem <- lm_robust(therm_1_fc1 ~ fc1_w2 + 
        alliance_defending_freedom_screener +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, 
        data = both_waves_s2[both_waves_s2$pid_alternative == "Democrat",])
#Republicans
fit7_s2_rep <- lm_robust(therm_1_fc1 ~ fc1_w2 + 
        alliance_defending_freedom_screener +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, 
        data = both_waves_s2[both_waves_s2$pid_alternative == "Republican",])
#Other
fit7_s2_other <- lm_robust(therm_1_fc1 ~ fc1_w2 + 
        alliance_defending_freedom_screener +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, 
        data = both_waves_s2[both_waves_s2$pid_alternative == "Independent/Other",])
```

```{r, echo = FALSE, results='asis'}
#Creating regression table
texreg(list(fit7_s2_dem, fit7_s2_rep, fit7_s2_other), include.ci = FALSE,
       custom.coef.names = c("Intercept", "Control", "Fact check",
          "Pre-treatment feeling thermometer", 
          "Male", "College graduate", 
          "High household income", "Age", "Religiously affiliated", "Monthly attendance",
          "Non-Hispanic White"),
       custom.model.names = c("Democrats", "Republicans", "Other"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Fact-checking the claim that abortion pills are dangerous does not have a statistically significant effect on Democrats’ opinions of Alliance Defending Freedom (0-to-100 scale)", 
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
omit.coef = "alliance_defending_freedom_screener|male|college_grad|income_100000|age|relig_affiliated|monthly_attend|non_hisp_white")
```

```{r, include = FALSE, message = FALSE}
#Seth Gruber - by partisanship
#Running models
fit8_s2_dem <- lm_robust(therm_1_fc2 ~ fc2_w2 + 
        gruber_screener +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2[both_waves_s2$pid_alternative == "Democrat",])
fit8_s2_rep <- lm_robust(therm_1_fc2 ~ fc2_w2 + 
        gruber_screener +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2[both_waves_s2$pid_alternative == "Republican",])
fit8_s2_other <- lm_robust(therm_1_fc2 ~ fc2_w2 + 
        gruber_screener +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2[both_waves_s2$pid_alternative == "Independent/Other",])
```

```{r, echo = FALSE, results='asis'}
#Creating regression table
texreg(list(fit8_s2_dem, fit8_s2_rep, fit8_s2_other), include.ci = FALSE,
       custom.coef.names = c("Intercept", "Control", "Fact check",
          "Pre-treatment feeling thermometer", 
          "Male", "College graduate", 
          "High household income", "Age", "Religiously affiliated", "Monthly attendance",
          "Non-Hispanic White"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Fact-checking the claim that contraception availability increases abortion demand low-
ers Democrats’ opinions of Seth Gruber (0-to-100 scale)", 
       custom.model.names = c("Democrats", "Republicans", "Other"),
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
omit.coef = "gruber_screener|male|college_grad|income_100000|age|relig_affiliated|monthly_attend|non_hisp_white")
```

```{r, include = FALSE, message = FALSE}
#Americans United For Life - by partisanship
#Running models
fit9_s2_dem <- lm_robust(therm_1_fc3 ~ fc3_w2 + 
        americans_united_screener +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, 
        data = both_waves_s2[both_waves_s2$pid_alternative == "Democrat",])
fit9_s2_rep <- lm_robust(therm_1_fc3 ~ fc3_w2 + 
        americans_united_screener +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, 
        data = both_waves_s2[both_waves_s2$pid_alternative == "Republican",])
fit9_s2_other <- lm_robust(therm_1_fc3 ~ fc3_w2 + 
        americans_united_screener +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, 
        data = both_waves_s2[both_waves_s2$pid_alternative == "Independent/Other",])
```

```{r, echo = FALSE, results='asis'}
#Creating regression table
texreg(list(fit9_s2_dem, fit9_s2_rep, fit9_s2_other), include.ci = FALSE,
       custom.coef.names = c("Intercept", "Control", "Fact check",
          "Pre-treatment feeling thermometer", 
          "Male", "College graduate", 
          "High household income", "Age", "Religiously affiliated", "Monthly attendance",
          "Non-Hispanic White"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Fact-checking the claim about the pregnant 10-year-old lowers Democrats' opinions of Americans United For Life (0-to-100 scale)", 
       custom.model.names = c("Democrats", "Republicans", "Other"),
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
omit.coef = "americans_united_screener|male|college_grad|income_100000|age|relig_affiliated|monthly_attend|non_hisp_white")
```

### Attitudes by religiosity

```{r, include = FALSE, message = FALSE}
#Alliance Defending Freedom - by religiosity
#Running models

#Low religiosity
fit10_s2_low_relig <- lm_robust(therm_1_fc1 ~ fc1_w2 + 
        alliance_defending_freedom_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        non_hisp_white, data = both_waves_s2[both_waves_s2$attend_cleaned == "Low",])
#Medium religiosity
fit10_s2_med_relig <- lm_robust(therm_1_fc1 ~ fc1_w2 + 
        alliance_defending_freedom_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        non_hisp_white, data = both_waves_s2[both_waves_s2$attend_cleaned == "Medium",])
#High religiosity
fit10_s2_high_relig <- lm_robust(therm_1_fc1 ~ fc1_w2 + 
        alliance_defending_freedom_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        non_hisp_white, data = both_waves_s2[both_waves_s2$attend_cleaned == "High",])
```

```{r, echo = FALSE, results='asis'}
#Creating regression table
texreg(list(fit10_s2_low_relig, fit10_s2_med_relig, fit10_s2_high_relig), include.ci = FALSE,
       custom.coef.names = c("Intercept", "Control", "Fact check",
          "Pre-treatment feeling thermometer", 
          "Partisanship", "Male", "College graduate", "High household income", "Age", 
          "Non-Hispanic White"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Fact-checking the claim that abortion pills are dangerous reduces the low religiosity
group’s opinions of Alliance Defending Freedom (0-to-100 scale)", 
       caption.above = TRUE, float.pos = "H",
       custom.model.names = c("Low religiosity", "Medium religiosity", "High religiosity"),
       single.row = TRUE,
       omit.coef = "alliance_defending_freedom_screener|pid_cleaned|male|college_grad|income_100000|age|relig_affiliated|non_hisp_white")
```

```{r, include = FALSE, message = FALSE}
#Seth Gruber - by religiosity
#Running models

#High religiosity
fit11_s2_high_relig <- lm_robust(therm_1_fc2 ~ fc2_w2 + 
        gruber_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        non_hisp_white, data = both_waves_s2[both_waves_s2$attend_cleaned == "High",])
#Medium religiosity
fit11_s2_med_relig <- lm_robust(therm_1_fc2 ~ fc2_w2 + 
        gruber_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        non_hisp_white, data = both_waves_s2[both_waves_s2$attend_cleaned == "Medium",])
#Low religiosity
fit11_s2_low_relig <- lm_robust(therm_1_fc2 ~ fc2_w2 + 
        gruber_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        non_hisp_white, data = both_waves_s2[both_waves_s2$attend_cleaned == "Low",])
```

```{r, echo = FALSE, results='asis'}
#Regression output (model fit4_s2_religiosity)
texreg(list(fit11_s2_low_relig, fit11_s2_med_relig, fit11_s2_high_relig), include.ci = FALSE,
       custom.coef.names = c("Intercept", "Control", "Fact check",
          "Pre-treatment feeling thermometer", 
          "Partisanship", "Male", "College graduate", "High household income", "Age",
          "Non-Hispanic White"),
       stars = c(0.05, 0.01, 0.001), 
       custom.model.names = c("Low religiosity", "Medium religiosity", "High religiosity"),
       caption = "Fact-checking the claim about contraception availability lowers the low religiosity group's ratings of Seth Gruber (0-to-100 scale)", 
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
       omit.coef = "gruber_screener|pid_cleaned|male|college_grad|income_100000|age|relig_affiliated|non_hisp_white")
```

```{r, include = FALSE, message = FALSE}
#Americans United For Life - by religiosity
#Running models

#Low religiosity
fit12_s2_low_relig <- lm_robust(therm_1_fc3 ~ fc3_w2 + 
        americans_united_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        non_hisp_white, data = both_waves_s2[both_waves_s2$attend_cleaned == "Low",])
#Medium religiosity
fit12_s2_med_relig <- lm_robust(therm_1_fc3 ~ fc3_w2 + 
        americans_united_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        non_hisp_white, data = both_waves_s2[both_waves_s2$attend_cleaned == "Medium",])
#High religiosity
fit12_s2_high_relig <- lm_robust(therm_1_fc3 ~ fc3_w2 + 
        americans_united_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        non_hisp_white, data = both_waves_s2[both_waves_s2$attend_cleaned == "High",])
```

```{r, echo = FALSE, results='asis'}
#Regression output
texreg(list(fit12_s2_low_relig, fit12_s2_med_relig, fit12_s2_high_relig), include.ci = FALSE,
       custom.coef.names = c("Intercept", "Control", "Fact check",
          "Pre-treatment feeling thermometer", 
          "Partisanship", "Male", "College graduate", "High household income", "Age",
          "Non-Hispanic White"),
       stars = c(0.05, 0.01, 0.001), 
       custom.model.names = c("Low religiosity", "Medium religiosity", "High religiosity"),
       caption = "Fact-checking the claim about the pregnant 10-year-old has a statistically insignificant effect on ratings of Americans United For Life (0-to-100 scale)", 
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
       omit.coef = "americans_united_screener|pid_cleaned|male|college_grad|income_100000|age|relig_affiliated|non_hisp_white")
```
### Other attitudes: abortion laws and penalties

```{r, include = FALSE, message = FALSE}
#Cleaning abortion laws measure
both_waves_s2$abortion_laws <- NA
both_waves_s2$abortion_laws[
  both_waves_s2$Q1...90_w2 == "By law, abortion should never be permitted."
  ] <- 1
both_waves_s2$abortion_laws[
  both_waves_s2$Q1...90_w2 == "The law should permit abortion only in case of rape, incest or when the woman's life is in danger."
  ] <- 2
both_waves_s2$abortion_laws[
  both_waves_s2$Q1...90_w2 == "The law should permit abortion for reasons other than rape, incest, or danger to the woman's life, but only after the need has been clearly established."
  ] <- 3
both_waves_s2$abortion_laws[
  both_waves_s2$Q1...90_w2 == "By law, a woman should always be able to obtain an abortion as a matter of personal choice."
  ] <- 4
```

```{r, include = FALSE, message = FALSE}
#Cleaning abortion penalties measure
both_waves_s2$Q2_1_cleaned <- NA
both_waves_s2$Q2_1_cleaned[
  both_waves_s2$Q2_1_w2 == "Should face penalties"
  ] <- 1
both_waves_s2$Q2_1_cleaned[
  both_waves_s2$Q2_1_w2 == "Should not face penalties"
  ] <- 0

both_waves_s2$Q2_2_cleaned <- NA
both_waves_s2$Q2_2_cleaned[
  both_waves_s2$Q2_2_w2 == "Should face penalties"
  ] <- 1
both_waves_s2$Q2_2_cleaned[
  both_waves_s2$Q2_2_w2 == "Should not face penalties"
  ] <- 0

both_waves_s2$Q2_3_cleaned <- NA
both_waves_s2$Q2_3_cleaned[
  both_waves_s2$Q2_3_w2 == "Should face penalties"
  ] <- 1
both_waves_s2$Q2_3_cleaned[
  both_waves_s2$Q2_3_w2 == "Should not face penalties"
  ] <- 0

both_waves_s2$Q2_4_cleaned <- NA
both_waves_s2$Q2_4_cleaned[
  both_waves_s2$Q2_4_w2 == "Should face penalties"
  ] <- 1
both_waves_s2$Q2_4_cleaned[
  both_waves_s2$Q2_4_w2 == "Should not face penalties"
  ] <- 0

both_waves_s2$abortion_penalties <-
  both_waves_s2$Q2_1_cleaned + both_waves_s2$Q2_2_cleaned +
  both_waves_s2$Q2_3_cleaned + both_waves_s2$Q2_4_cleaned
```

```{r, include = FALSE, warning = FALSE}
#Creating new variable for whether someone was
  #assigned to misinformation, control,
  #or fact check condition of some sort
both_waves_s2$fc_all <- NA
both_waves_s2$fc_all[
  both_waves_s2$fc1_w2 == "mis" |  
  both_waves_s2$fc2_w2 == "mis" | 
  both_waves_s2$fc3_w2 == "mis"] <- "mis"
both_waves_s2$fc_all[
  both_waves_s2$fc1_w2 == "c" |  
  both_waves_s2$fc2_w2 == "c" | 
  both_waves_s2$fc3_w2 == "c"] <- "c"
both_waves_s2$fc_all[
  both_waves_s2$fc1_w2 == "fc" |  
  both_waves_s2$fc2_w2 == "fc" | 
  both_waves_s2$fc3_w2 == "fc"] <- "fc"
```

```{r, include = FALSE, message = FALSE}
#Setting misinformation group as reference category
both_waves_s2$fc_all <- 
  as.factor(both_waves_s2$fc_all)
both_waves_s2$fc_all <- 
  relevel(both_waves_s2$fc_all, ref="mis")
```

```{r, include = FALSE, message = FALSE}
#Creating subsets for people who were asked
  #about first, second, and third factual beliefs
both_waves_s2_fc1 <-
  subset(both_waves_s2, fc1_w2 %in% c("mis", "c", "fc"))
both_waves_s2_fc2 <-
  subset(both_waves_s2, fc2_w2 %in% c("mis", "c", "fc"))
both_waves_s2_fc3 <-
  subset(both_waves_s2, fc3_w2 %in% c("mis", "c", "fc"))
```

```{r, include = FALSE, message = FALSE}
#Running models

#FC1 group
fit13_s2 <- lm_robust(abortion_laws ~ fc_all + abortion_laws_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2_fc1)
#FC2 group
fit14_s2 <- lm_robust(abortion_laws ~ fc_all + abortion_laws_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2_fc2)
#FC3 group
fit15_s2 <- lm_robust(abortion_laws ~ fc_all + abortion_laws_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2_fc3)
```



```{r, echo = FALSE, results='asis'}
#Creating regression table
texreg(list(fit13_s2, fit14_s2, fit15_s2), include.ci = FALSE,
       custom.model.names=c("FC1", "FC2", "FC3"),
       custom.coef.names = c("Intercept", "Control", "Fact check", "Pre-treatment abortion laws attitudes", 
          "Partisanship", "Male", "College graduate", "High household income", "Age", "Religiously affiliated", "Monthly attendance",
          "Non-Hispanic White"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Effect of fact check on attitudes about abortion laws (1-to-4 scale)", 
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
       omit.coef = "abortion_laws_screener|pid_cleaned|male|college_grad|income_100000|age|relig_affiliated|monthly_attend|non_hisp_white")
```

```{r, include = FALSE, message = FALSE}
#Running models

#FC1 group
fit16_s2 <- lm_robust(abortion_penalties ~ fc_all + abortion_penalties_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2_fc1)
#FC2 group
fit17_s2 <- lm_robust(abortion_penalties ~ fc_all + abortion_penalties_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2_fc2)
#FC3 group
fit18_s2 <- lm_robust(abortion_penalties ~ fc_all + abortion_penalties_screener + pid_cleaned +
        male + college_grad + income_100000 + age +
        relig_affiliated + monthly_attend + non_hisp_white, data = both_waves_s2_fc3)
```

```{r, echo = FALSE, results='asis'}
#Creating regression table
texreg(list(fit16_s2, fit17_s2, fit18_s2), include.ci = FALSE,
       custom.model.names=c("FC1", "FC2", "FC3"),
       custom.coef.names = c("Intercept", "Control", "Fact check", "Pre-treatment abortion penalties attitudes", 
          "Partisanship", "Male", "College graduate", "High household income", "Age", "Religiously affiliated", "Monthly attendance",
          "Non-Hispanic White"),
       stars = c(0.05, 0.01, 0.001), 
       caption = "Effect of fact check on attitudes about abortion penalties (0-to-4 scale)", 
       caption.above = TRUE, float.pos = "H",
       single.row = TRUE,
       omit.coef = "abortion_penalties_screener|pid_cleaned|male|college_grad|income_100000|age|relig_affiliated|monthly_attend|non_hisp_white")
```

## H1 graph (factual beliefs)

```{r, include = FALSE, message = FALSE}
#Creating marginal effects data frame
#Looking at effects of misinformation and fact-checks on factual beliefs
ma_fit1_s2 <- margins(fit1_s2)
ma_2_fit1_s2 <- summary(ma_fit1_s2)
ma_2_fit1_s2$var <- 1:11

ma_fit2_s2 <- margins(fit2_s2)
ma_2_fit2_s2 <- summary(ma_fit2_s2)
ma_2_fit2_s2$var <- 1:11

ma_fit3_s2 <- margins(fit3_s2)
ma_2_fit3_s2 <- summary(ma_fit3_s2)
ma_2_fit3_s2$var <- 1:11

ma_combined_s2 <- rbind(ma_2_fit1_s2[5,], ma_2_fit2_s2[5,], ma_2_fit3_s2[5,])
ma_combined_s2$var <- 1:3

ma_combined_s2_2 <- rbind(ma_2_fit1_s2[4,], ma_2_fit2_s2[4,], ma_2_fit3_s2[4,])
ma_combined_s2_2$var <- 1:3

ma_combined_s2_2$AME <- -ma_combined_s2_2$AME
ma_combined_s2_2$lower <- -ma_combined_s2_2$lower
ma_combined_s2_2$upper <- -ma_combined_s2_2$upper
colnames(ma_combined_s2_2) <- c("factor", "AME", "SE", "z", "p", "upper", "lower", "var")

ma_combined_s2$factor <- NULL
ma_combined_s2_2$factor <- NULL
ma_combined_s2$effect <- "Fact check"
ma_combined_s2_2$effect <- "Misinformation"
ma_combined_s2_2 <-
  ma_combined_s2_2 %>%
  select(AME, SE, z, p, lower, upper, var, effect)

ma_combined_s2_v1 <-
  rbind(ma_combined_s2, ma_combined_s2_2)
colnames(ma_combined_s2_v1) <-
  c("AME", "SE", "z", "p", "lower", "upper", "var", "Effect")
```

```{r, include = FALSE, message = FALSE}
#Saving marginal effects (factual beliefs) data frame
save(ma_combined_s2_v1, file = "ma_combined_attitudes_s2_v1.RData")
```

## H2 graph (attitudinal beliefs)

```{r, include = FALSE, message = FALSE}
#Creating marginal effects data frame
#Looking at effects of fact-checks on attitudinal beliefs
ma_fit4_s2 <- margins(fit4_s2)
ma_2_fit4_s2 <- summary(ma_fit4_s2)
ma_2_fit4_s2$var <- 1:11

ma_fit5_s2 <- margins(fit5_s2)
ma_2_fit5_s2 <- summary(ma_fit5_s2)
ma_2_fit5_s2$var <- 1:11

ma_fit6_s2 <- margins(fit6_s2)
ma_2_fit6_s2 <- summary(ma_fit6_s2)
ma_2_fit6_s2$var <- 1:11

ma_combined_3_s2 <- rbind(ma_2_fit4_s2[5,], ma_2_fit5_s2[4,], ma_2_fit6_s2[5,])
ma_combined_3_s2$var <- 1:3

ma_combined_4_s2 <- rbind(ma_2_fit4_s2[4,], ma_2_fit5_s2[3,], ma_2_fit6_s2[4,])
ma_combined_4_s2$var <- 1:3

ma_combined_4_s2$AME <- -ma_combined_4_s2$AME
ma_combined_4_s2$lower <- -ma_combined_4_s2$lower
ma_combined_4_s2$upper <- -ma_combined_4_s2$upper
colnames(ma_combined_4_s2) <- c("factor", "AME", "SE", "z", "p", "upper", "lower", "var")

ma_combined_3_s2$factor <- NULL
ma_combined_4_s2$factor <- NULL
ma_combined_3_s2$effect <- "Fact check"
ma_combined_4_s2$effect <- "Misinformation"
ma_combined_4_s2 <-
  ma_combined_4_s2 %>%
  select(AME, SE, z, p, lower, upper, var, effect)

ma_combined_s2_v2 <-
  rbind(ma_combined_3_s2, ma_combined_4_s2)
colnames(ma_combined_s2_v2) <-
  c("AME", "SE", "z", "p", "lower", "upper", "var", "Effect")

ma_combined_s2_v2 <- ma_combined_s2_v2[1:3,]
```

```{r, include = FALSE, message = FALSE}
#Saving marginal effects (attitudinal beliefs) data frame
save(ma_combined_s2_v2, file = "ma_combined_attitudes_s2_v2.RData")
```

## Balance tables

```{r, include = FALSE, message = FALSE}
#Setting up balance frame for respondents who received FC1
#Selecting just some variables and renaming some of them
#Recoding the `Abortion pills FC` variable
abortion_s2_fc1_v2 <- both_waves_s2_fc1 %>%
  select(fc1_w2, age, male, non_hisp_white, college_grad, income_100000, 
         pid_cleaned)
colnames(abortion_s2_fc1_v2) <-
  c("Abortion pills FC", "Age", "Share who are male", 
    "Share who are non-Hispanic White", 
    "Share who are college graduates", 
    "Share who have household incomes of $100,000+",
    "Partisanship (7-point scale)")
abortion_s2_fc1_v2$`Abortion pills FC` <-
  as.character(abortion_s2_fc1_v2$`Abortion pills FC`)
abortion_s2_fc1_v2$`Abortion pills FC`[
abortion_s2_fc1_v2$`Abortion pills FC` == "c"
  ] <- "Control"
abortion_s2_fc1_v2$`Abortion pills FC`[
abortion_s2_fc1_v2$`Abortion pills FC` == "fc"
  ] <- "Fact-check"
abortion_s2_fc1_v2$`Abortion pills FC`[
  abortion_s2_fc1_v2$`Abortion pills FC` == "mis"
  ] <- "Misinformation"
```

```{r, include = FALSE, message = FALSE}
#Setting up balance frame for respondents who received FC2
#Selecting just some variables and renaming some of them
#Recoding the `Contraception FC` variable
abortion_s2_fc2_v2 <- both_waves_s2_fc2 %>%
  select(fc2_w2, age, male, non_hisp_white, college_grad, income_100000, 
         pid_cleaned)
colnames(abortion_s2_fc2_v2) <-
  c("Contraception FC", "Age", "Share who are male", 
    "Share who are non-Hispanic White", 
    "Share who are college graduates", 
    "Share who have household incomes of $100,000+",
    "Partisanship (7-point scale)")
abortion_s2_fc2_v2$`Contraception FC` <-
  as.character(abortion_s2_fc2_v2$`Contraception FC`)
abortion_s2_fc2_v2$`Contraception FC`[
abortion_s2_fc2_v2$`Contraception FC` == "c"
  ] <- "Control"
abortion_s2_fc2_v2$`Contraception FC`[
abortion_s2_fc2_v2$`Contraception FC` == "fc"
  ] <- "Fact-check"
abortion_s2_fc2_v2$`Contraception FC`[
  abortion_s2_fc2_v2$`Contraception FC` == "mis"
  ] <- "Misinformation"
```

```{r, include = FALSE, message = FALSE}
#Setting up balance frame for respondents who received FC3
#Selecting just some variables and renaming some of them
#Recoding the `10-year-old FC` variable
abortion_s2_fc3_v2 <- both_waves_s2_fc3 %>%
  select(fc3_w2, age, male, non_hisp_white, college_grad, income_100000, 
         pid_cleaned)
colnames(abortion_s2_fc3_v2) <-
  c("10-year-old FC", "Age", "Share who are male", 
    "Share who are non-Hispanic White", 
    "Share who are college graduates", 
    "Share who have household incomes of $100,000+",
    "Partisanship (7-point scale)")
abortion_s2_fc3_v2$`10-year-old FC` <-
  as.character(abortion_s2_fc3_v2$`10-year-old FC`)
abortion_s2_fc3_v2$`10-year-old FC`[
abortion_s2_fc3_v2$`10-year-old FC` == "c"
  ] <- "Control"
abortion_s2_fc3_v2$`10-year-old FC`[
abortion_s2_fc3_v2$`10-year-old FC` == "fc"
  ] <- "Fact-check"
abortion_s2_fc3_v2$`10-year-old FC`[
  abortion_s2_fc3_v2$`10-year-old FC` == "mis"
  ] <- "Misinformation"
```

First fact-check (abortion pills):

```{r, include = FALSE, message = FALSE}
#Creating first balance table
abortion_s2_fc1_v3 <- balance_table(abortion_s2_fc1_v2, "Abortion pills FC")
colnames(abortion_s2_fc1_v3) <- c("Variable", "Control", "Fact check", "Misinfo", "p-value (c vs fc)", "p-value (c vs mis)")
```

```{r, echo = FALSE, results='asis'}
#Printing out results of first balance table
print(xtable(abortion_s2_fc1_v3), size = "tiny")
```
Second fact-check (contraception):

```{r, include = FALSE, message = FALSE}
#Creating second balance table
abortion_s2_fc2_v3 <- balance_table(abortion_s2_fc2_v2, "Contraception FC")
colnames(abortion_s2_fc2_v3) <- c("Variable", "Control", "Fact check", "Misinfo", "p-value (c vs fc)", "p-value (c vs mis)")
```


```{r, echo = FALSE, results='asis'}
#Printing out results from second balance table
print(xtable(abortion_s2_fc2_v3), size = "tiny")
```

Third fact-check (10-year-old):

```{r, include = FALSE, message = FALSE}
#Creating third balance table
abortion_s2_fc3_v3 <- balance_table(abortion_s2_fc3_v2, "10-year-old FC")
colnames(abortion_s2_fc3_v3) <- c("Variable", "Control", "Fact check", "Misinfo", "p-value (c vs fc)", "p-value (c vs mis)")
```

```{r, echo = FALSE, results='asis'}
#Printing out results from third balance table
print(xtable(abortion_s2_fc3_v3), size = "tiny")
```